\documentclass[12pt,a4paper,oneside]{report}

\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{newtxtext,newtxmath}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{amsmath,amssymb}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\usepackage{url}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    citecolor=black,
    urlcolor=blue
}

\onehalfspacing

\newcommand{\methodname}{EARR-TOPSIS}
\newcommand{\fullmethodname}{Entropy-Aware Reliability-Weighted Robust Fuzzy TOPSIS}
\newcommand{\thesistitle}{\fullmethodname{} for Bias-Resistant Group Decision-Making}
\newcommand{\studentname}{Fahim Afridi}
\newcommand{\university}{BRAC University}
\newcommand{\department}{Department of Computer Science and Engineering}

\begin{document}

\begin{titlepage}
    \centering
    \vspace*{1cm}
    {\Large \university\par}
    \vspace{0.3cm}
    {\large \department\par}
    \vspace{2cm}
    {\Huge\bfseries \thesistitle\par}
    \vspace{1.5cm}
    {\Large Thesis/Dissertation Report\par}
    \vspace{1.5cm}
    {\large Submitted by\par}
    \vspace{0.3cm}
    {\Large\bfseries \studentname\par}
    \vspace{0.8cm}
    {\large Student ID: \textit{insert student ID}\par}
    \vspace{1.2cm}
    {\large Supervisor: \textit{insert supervisor name}\par}
    \vfill
    {\large May 2026\par}
\end{titlepage}

\pagenumbering{roman}

\chapter*{Declaration}
I hereby declare that this thesis/dissertation is based on my original research work, except where due acknowledgement has been made. The work has not been submitted previously, in whole or in part, for any degree or diploma at any other institution.

\vspace{2cm}
\noindent Signature: \rule{6cm}{0.4pt}\\
\noindent Date: \rule{4cm}{0.4pt}

\chapter*{Acknowledgements}
I would like to express my sincere gratitude to my supervisor and faculty members at BRAC University for their guidance, feedback, and encouragement throughout this research. I also acknowledge the open datasets and prior research literature that made the experimental evaluation possible.

\chapter*{Abstract}
Group decision-making methods based on fuzzy TOPSIS are widely used when multiple decision makers evaluate alternatives under uncertainty. However, classical fuzzy TOPSIS typically assumes that decision-maker inputs are sincere and does not explicitly defend against coordinated biased ratings. This thesis investigates the vulnerability of fuzzy TOPSIS under targeted decision-maker contamination and proposes a reliability-aware ensemble framework for bias-resistant group decision-making.

The research develops a progression of methods from classical fuzzy TOPSIS to bootstrap bagging, reliability filtering, reliability-weighted bagging, reliability-weighted aggregation, and a final entropy-aware reliability-weighted ensemble method named \methodname. The final proposed framework uses multiple reliability signals, including entropy, variance consistency, and clone/agreement-pattern detection, then combines reliability-weighted sampling, reliability-weighted fuzzy aggregation, and bag-quality weighting. Experiments are conducted on synthetic datasets and real/pseudo-real datasets converted into fuzzy group-decision panels. The evaluation includes clean stability, contaminated robustness, attack-fraction curves, external comparator baselines, confidence intervals, pairwise target-error tests, and runtime analysis.

The results show that standard fuzzy TOPSIS and plain bootstrap bagging are vulnerable to coordinated target promotion. In the main attack-fraction experiments, reliability-weighted bagging and reliability-weighted aggregation preserved the clean target rank through 40\% effective structured contamination, while \methodname{} preserved the clean target rank across all tested structured contamination levels up to 60\%. External comparators, including median aggregation, trimmed-mean aggregation, MAD-consensus filtering, individual-Borda aggregation, and a Huang--Li group-ideal TOPSIS adaptation, were less robust under high structured contamination. The work does not claim universal robustness against all strategic adversaries; adaptive human-mimic attacks remain a limitation. The contribution is therefore framed as robustness against structured, statistically distinguishable coordinated manipulation in fuzzy TOPSIS group decision-making.

\tableofcontents
\listoftables
\listoffigures

\clearpage
\pagenumbering{arabic}

\include{chapters/01_introduction}
\include{chapters/02_literature_review}
\include{chapters/03_methodology}
\include{chapters/04_experimental_design}
\include{chapters/05_results}
\include{chapters/06_discussion}
\include{chapters/07_conclusion}

\appendix
\include{chapters/appendix_public_demo}

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
