\chapter*{Abstract}

Group decision-making methods based on fuzzy TOPSIS are widely used when multiple decision makers evaluate alternatives under uncertainty. However, classical fuzzy TOPSIS usually assumes sincere decision-maker input and does not explicitly defend against coordinated biased ratings. This thesis investigates the vulnerability of fuzzy TOPSIS under targeted decision-maker contamination and proposes a reliability-aware ensemble framework for bias-resistant group decision-making.

The research develops a progression of methods from classical fuzzy TOPSIS to bootstrap bagging, reliability filtering, reliability-weighted bagging, reliability-weighted aggregation, and a final entropy-aware reliability-weighted ensemble method named \methodname. The final proposed framework uses multiple reliability signals, including entropy, variance consistency, and clone/agreement-pattern detection, then combines reliability-weighted sampling, reliability-weighted fuzzy aggregation, and bag-quality weighting. Experiments are conducted on synthetic datasets and real/pseudo-real datasets converted into fuzzy group-decision panels. The evaluation includes clean stability, contaminated robustness, attack-fraction curves, external comparator baselines, confidence intervals, paired target-error tests, and runtime analysis.

The results show that standard fuzzy TOPSIS and plain bootstrap bagging are vulnerable to coordinated target promotion. In the main attack-fraction experiments, reliability-weighted bagging and reliability-weighted aggregation preserved the clean target rank through 40 percent effective structured contamination, while \methodname{} preserved the clean target rank across all tested structured contamination levels up to 60 percent. External comparators, including median aggregation, trimmed-mean aggregation, MAD-consensus filtering, individual-Borda aggregation, and a Huang--Li group-ideal TOPSIS adaptation, were less robust under high structured contamination. The work does not claim universal robustness against all strategic adversaries; adaptive human-mimic attacks remain a limitation. The contribution is therefore framed as robustness against structured, statistically distinguishable coordinated manipulation in fuzzy TOPSIS group decision-making.
